### 2016-04-22 hoist.tex
Added advantages of code-hoisting

>>>>

\section{Hoisting bottom up with optimistic approach}
Optimistic means collect the set of all potential redundancies and then discard the bad ones.

Bottom up:
Sort the basic blocks of potentially redundant computations based on DFS-in numbers.
Then start evaluating the safety checks for first two, if good then move to second one. That way we can even
partially hoist computations should we find that we cannot remove all the redundant computations.

We can also split the set of to partially hoist multiple times, if hoisting globally is not possible.

In the case when more than one computation from the same basic block shows up as redundant.
e.g.
BB1
load a;
....
store .;
....
load a;

BB2
load a

BB0 -> BB1
BB0 -> BB2

In this case both the loads from BB1 will show up as redundant (according to the current algorithm), but the complete
hoising will fail as the second load in BB1 is not safe to hoist. By following the bottom-up approach, the sorted list
of BBs will appear like this:

{ BB1, BB2(first load), BB2(second load) }

Now we will start evaluating the safety of BB1-l1 and BB2-l2 which will pass, then BB12-l1 and BB2-l2 will fail.
So we can revert back to BB12-l1 and hoist them to BB0. Doing the top down approach and finding the partial set
to hoist instructions partially would result in a combinatorial explosion.

GCC: 23286 has interesting test cases.

\section{Enabling LICM by code-hoisting}
loop:
if (a)
  i1;
else
  i1;

Here i1 is redundant and can be hoisted out of loop. But the LICM will not do because it does not reason about instructions in the conditional.
By code-hoisting i1 will be hoisted out of conditional which will benefit the LICM.

\section{Improving the Inliner heuristics}
Reducing the number of instructions also reduces the inline cost and hence improves the inliner heuristics.

\section{Improving vectorization}
It will also benefit vectorizer by reducing the number
of basic blocks, should all the instructions in conditional get hoisted.
